|

### 2020-07-28 paper.Rmd
Better diagram.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(gridExtra)
library(ggforce)
library(tourr)
```

@@

XXX maybe a better picture is going from a 2D circle to a 1D projection?

```{r, out.width="40%", fig.align = "center"}

@@

ggplot() +
  geom_circle(aes(x0= 0, y0=0, r = 1)) +
  geom_area(aes(x=x, y=yp), fill = "red", alpha = 0.5) +
  geom_area(aes(x=x, y=ym), fill = "red", alpha = 0.5) +
  geom_area(aes(x=x_outer1, y=yp_outer1), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer1, y=ym_outer1), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer2, y=yp_outer2), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer2, y=ym_outer2), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer1-1+xp, y=yp_outer1), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer1-1+xp, y=ym_outer1), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer2+1-xp, y=yp_outer2), fill = "blue", alpha = 0.5) +
  geom_area(aes(x=x_outer2+1-xp, y=ym_outer2), fill = "blue", alpha = 0.5) +
  theme_classic() +
  xlab("x") + ylab("y") +
  coord_fixed()

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(gridExtra)
library(ggforce)
library(tourr)
library(latex2exp)
```

@@

```{r, out.width="30%", fig.cap="Diagram illustrating volume vs projected volume for a 3D sphere. The full sphere has volume $V(R, p)$. Within a radius $r$ the sphere contains the reduced volume $V(r; p, R)$, but the projected volume within a radius $r$ in a 2D plane is much larger, $V_{2D}(r; p ,R)$.", fig.align = "center"}

@@

ggplot() +
  geom_circle(aes(x0= 0, y0=0, r = 1)) +
  geom_circle(aes(x0= 0, y0=0, r = xp)) +
  geom_ellipse(aes(x0 = 0, y0 = 0, a = 1, b = 0.2, angle = 0)) +
  geom_ellipse(aes(x0 = 0, y0 = 0, a = xp, b = xp/5, angle = 0)) +
  geom_area(aes(x=x, y=yp), fill = "red", alpha = 0.5) +
  geom_area(aes(x=x, y=ym), fill = "red", alpha = 0.5) +
  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 0),
               size = 0.5, arrow = arrow(length = unit(0.1, "inches"))) +
  annotate("text", x = 0.5, y = 0.05, label="R") +
  geom_segment(aes(x = 0, y = 0, xend = xp, yend = 0),
               size = 0.5, arrow = arrow(length = unit(0.1, "inches"))) +
  annotate("text", x = xp/2, y = 0.05, label="r") +
  annotate("text", x = 0, y = 0.5, label=TeX("$V_{2D}(r; p, R)$")) + 
  annotate("text", x = -0.2, y = 0.05, label=TeX("$V(r; p, R)$")) + 
  annotate("text", x = 0.5, y = 0.25, label="V(R,p)") +
  theme_void() +
  coord_fixed()
